---
title: "Assignment 5"
author: "Submitted by Ilka Weichert (Student ID: 4161194)"
date: "February 16th, 2021"
output: 
  html_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

I worked on my own. I hereby assure that my submission is in line with the 
*Code of Conduct* outlined on the lecture slides.

## General setup

Note that task descriptions are printed in bold letters. Only the descriptions
that are important for the actual operations are included.

Before I start the project, I clear my workspace.

```{r packages, message=FALSE, warning=F}
rm(list = ls())  # clear workspace
```

## Exercise 1: Setting up a new GitHub repository

**Register on github.com in case you have not done this already.**

I register on github.com choosing ilkaweichert as my user name.

**Initialize a new public repository for this assignment on GitHub.**

I set up a new public repository called "dspm_assignmentV".

**For the following exercises of this assignment, follow the standard Git **
**workflow (i.e., pull the latest version of the project to your local computer,**
**then stage, commit, and push all the modifications that you make throughout **
**the project). Every logical programming step should be well documented on**
**GitHub with a meaningful commit message, so that other people (e.g., your **
**course instructor) can follow understand the development history. You can to**
**do this either using Shell commands or a Git GUI of your choice.**

In the following exercises I make sure to follow the standard Git workflow and
document each logical programming step using R Studio. However, when working at
the ``for`` loop for exercise 4, I'm running into a problem since somehow I 
merged the branch "main" (probably by ticking the box for "Amend previous 
comment"). Therefore, the commits identified by 
4281530c61ec8b550a13d8cd50dbc697e379bdae to 
c3f40420e4080261f1c4c86ebb0b4f46037c93b1 might be confusing to look at.

**In the HTML file that you submit, include the hyperlink to the project **
**repository (e.g., ht tps:// github.com/yourUserName/ yourProjectName)**

The hyperlink to the project repository reads 
https://github.com/ilkaweichert/dspm_assignmentV.git

## Exercise 2: Getting to know the API

**Visit the documentation website for the API provided by ticketmaster.com.**

I visit the indicated documentation website for the ticketmaster.com API.

**Familiarize yourself with the features and functionalities of the Ticketmaster**
**Discovery API. Have a particular look at rate limits.**

I familiarize myself with the Ticketmaster Discovery API. The rate limit is set
at 5 requests per second. Each API key can request 5,000 API calls every day.

**Within the scope of this assignment, you do not have to request your own API **
**key. Instead retrieve a valid key from the API Explorer. This API key enables**
**you to perform the GET requests needed throughout this assignment.**

I retrieve a valid API key from the API Explorer.

**Even though this API key is not secret per se (it is publicly visible on the** 
**API Explorer website), please comply to the common secrecy practices discussed**
**in the lecture and the tutorial: Treat the API key as a secret token. Your **
**API key should neither appear in the code that you are submitting nor in your**
**public GitHub repository.**

I store the just retrieved API key in another R script and will refer to it by 
calling this script whenever needed so that the key itself does not appear in my
code nor my public GitHub repository.

```{r source_api_key}

# source API key from another R script
source("C:/Users/Ilka/UT Cloud/Theresa Veer - Promotion (Ilka Weichert)/Weiterbildung/R/Data Science Project Management/WS 20_21/Assignments/Assignment 5/api_key.R")

```

## Exercise 3: Interacting with the API - the basics

**Load the packages needed to interact with APIs using R.**

I load the packages which I need to interact with APIs using R. Note that first
especially the ``httr`` and the ``jsonlite`` package are needed to start working
with the ticketmaster API.

```{r load_packages}

# load packages
library(httr)      #  implementing http methods in R
library(jsonlite)  #  convert JSON object into R object
library(rlist)     #  working with list objects
library(tidyverse) #  set of packages that work in harmony

```

**Perform a first GET request, that searches for event venues in Germany **
**(countryCode = "DE"). Extract the content from the response object and **
**inspect the resulting list. Describe what you can see.**

I perform a first GET request searching for event venues in Germany. For this, I
use the root API https://app.ticketmaster.com/discovery/v2/ given at 
https://developer.ticketmaster.com/products-and-docs/apis/discovery-api/v2/#search-venues-v2
and add "/venues" to find information on the different venues. I then add the 
json extension and include the country code for Germany. By using ``paste()`` to
add the API key stored in ``api_key`` I make sure, that I do not have to 
directly include it in this file. I store the content in an object called
``german_event_venues``, call the object and check its status running 
``status_code`` to make sure that everything worked fine. The status code of 200
tells me that the server has successfully received my request.

When checking the list object ``german_event_venues`` I notice that I received a
list with 10 entries. The first one shows the URL and the second one again shows 
the status of the GET command which is 200. The entry which actually is most 
interesting to me is the one called “content” which is still stored in a 
machine-readable but not human-readable format.

```{r German_venues}

# store content on German event venues
german_event_venues <- 
  GET(paste("https://app.ticketmaster.com/discovery/v2/venues.json?countryCode=DE&locale=*&apikey=", api_key, sep = ""))

# call object
german_event_venues

# check status
status_code(german_event_venues)

```

**Extract the name, the city, the postalCode and address, as well as the url **
**and the longitude and latitude of the venues to a data frame.**

First of all, I extract the information stored in the list object ``content`` in
``german_event_venues`` by calling ``fromJSON()`` in combination with 
``content()`` and specifying the type as "text" and store it in an object called
``german_event_venues_reduced``. I do so to avoid any potential errors and to 
make sure that the response object is correctly identified as a JSON-object.
In a second step, I extract the city, postal code, address, URL, longitude and
latitude of the ventures and store them in a ``data.frame`` by calling 
``as.data.frame()`` in combination with ``cbind()`` combining the respective
list objects. I then adjust the column names by running ``setNames()``. Lastly, 
I call ``glimpse()`` on ``venue_data`` and compare the resulting structure with
the one given in the assignment instructions. The structure is identical. 

```{r extract_information}

# store response content
german_event_venues_reduced <-
  fromJSON(content(german_event_venues, as = "text"))[["_embedded"]][["venues"]]

# extract sought-after information
venue_data <-
  as.data.frame(cbind(german_event_venues_reduced$name, 
                      german_event_venues_reduced$city,
                      german_event_venues_reduced$postalCode,
                      german_event_venues_reduced$address,
                      german_event_venues_reduced$url,
                      german_event_venues_reduced$location)
  )

# adjust column names
venue_data <- 
  setNames(
    venue_data,
    c(
      "name",
      "city", 
      "postalCode", 
      "address", 
      "url", 
      "longitude", 
      "latitude")
    )

# adjust variable types for longitude and latitude
venue_data$longitude <-
  as.double(venue_data$longitude)
venue_data$latitude <-
  as.double(venue_data$latitude)


# check data 
glimpse(venue_data)
# note that the structure is the same compared to example in assignment but the
# content not necessarily. Problem?
```
## Exercise 4: Interacting with the API - advanced

**Have a closer look at the list element named page. Did your GET request from**
**exercise 3 return all event locations in Germany? Obviously not - there are **
**of course much more venues in Germany than those contained in this list. Your**
**GET request only yielded the first results page containing the first 20 out of**
**several thousands of venues.**

Checking the list element "page" I notice that by now I only stored 20 venues in
R. They all come from the first results page, however, there are 238 results 
pages and 4,743 venues in total. On each page there a 20 entries. Hence, there
are 237 pages with 20 entries and a further page with only 3 entries.

```{r check_list_elements}

# store response object anew to be able to exctract information other than content
german_event_venues_pages <-
  fromJSON(content(german_event_venues, as = "text"))

# check number of total pages
n_page <- german_event_venues_pages[["page"]][["totalPages"]]

# check number of total entries
german_event_venues_pages[["page"]][["totalElements"]]

# check number of entries on each page
german_event_venues_pages[["page"]][["size"]]

# check number of entries on last page
page_number <- floor(n_page/20)

missing_entries <- n_page - 20 * floor(n_page/20)

```

**Check the API documentation under the section Venue Search. How can you **
**request the venues from the remaining results pages?**

Having a look at the section Venue Search in the API documentation I realize
that I can specify the page number in the URL that I use for scraping the data.

**Write a for loop that iterates through the results pages and performs a GET**
**request for all venues in Germany. After each iteration, extract the seven**
**variables name, city, postalCode, address, url, longitude, and latitude. Join**
**the information in one large data frame.**

```{r page_loop}

full_venue_data <- data.frame(
  name  = character(n_page),
  city   = character(n_page),
  postalCode = integer(n_page),
  address   = character(n_page),
  url = character(n_page),
  longitude = numeric(n_page),
  latitutde = numeric(n_page),
  stringsAsFactors = F
  )

part_venues <- 
  GET("https://app.ticketmaster.com/discovery/v2/venues.json?",
      query = list(apikey = api_key,
                   countryCode = "DE",
                   locale = "*"))
  
german_venues <-
  content(part_venues)[["_embedded"]]


german_venues <-
  fromJSON(content(part_venues, as = "text"))[["_embedded"]][["venues"]]
# works but does not what it should
full_venue_data[(20 * 1 - 19):(20 * 1), ] <- list.stack(german_venues$venues[["location"]])


check <- list.stack(german_venues$location)


# doesn't work    
full_venue_data[(20 * 1 - 19):(10 * 1), ] <- german_venues %>%
  select(name, city, postalCode, address, url, list.stack(venues$location))

full_venue_data[(20 * 1 - 19):(10 * 1), ] <- german_venues %>%
  select(1, 5, 10, 13, 14, 15)


#Looping function to get a single string, separating values by commas for those values in the form of lists 
makeSingleStringFromList <- function(SomeList) {
    #If list is empty return NA
    if (length(SomeList) == 0) {
        NA
    } else {
        # Create array with the length of the list
        myArray <- array(data = NA, dim = length(SomeList), dimname = NULL)
        #Loop through list and add individual values to indexed position within array
        for (i in 1:length(SomeList)) {
            myArray[i] <- SomeList[i]
        }
        #Collapse individual values into one string
        singleString <- paste(myArray, collapse = ",")
        #Return string
        singleString
    }
}

#Another helper function to loop through a list within a list
makeSingleStringFromListWithinList <- function(SomeList) {
    #If list is empty return NA
    if (length(SomeList) == 0 | is.null(SomeList)) {
        NA
    } else {
        myArray <- array(data = NA, dim = length(SomeList), dimname = NULL)
        for (i in 1:length(SomeList)) {
            myArray[i] <- makeSingleStringFromList(SomeList[[i]]$value)
        }
        #Collapse individual values into one string
        singleString <- paste(myArray, collapse = ";")
        #Return string
        singleString
    }
}


response = GET(paste("https://app.ticketmaster.com/discovery/v2/venues.json?countryCode=DE&locale=*&apikey=", api_key, sep = ""))
    if (response$status_code == 200) { #then go on to get Content
        data <- fromJSON(rawToChar(response$content)) 
        
        #Loop through lists and make into single strins separated by commas
        name <- makeSingleStringFromList(data$embedded$venues$name)
        city <- makeSingleStringFromListWithinList(data$embedded$venues$city$name)
        postalCode <- makeSingleStringFromList(data$embedded$venues$postalCode)
        address <- makeSingleStringFromListWithinList(data$embedded$venues$address$line1)
        url <- makeSingleStringFromList(data$embedded$venues$url)
        locale <- makeSingleStringFromList(data$embedded$venues$locale)
        longitude <- makeSingleStringFromListWithinList(data$embedded$venues$location$longitude)
        latitude <- makeSingleStringFromListWithinList(data$embedded$venues$location$latitude)
        
        ticketmaster_data <- as.data.frame(
          name,
          city,
          postalCode,
          address,
          url,
          locale,
          longitude,
          latitude
        )
    }


for (i in page_number) {
  full_venue_data <-
    part_venues <- GET("https://app.ticketmaster.com/discovery/v2/venues.json?",
                       query = list(apikey = api_key,
                                    countryCode = "DE",
                                    locale = "*",
                                    page = i))
  
    german_venues <-
    fromJSON(content(part_venues, as = "text"))[["_embedded"]][["venues"]]
    
    full_venue_data[(20 * i - 19):(20 * i), ] <- list.stack(german_venues$embedded)
    
  Sys.sleep(0.2)
}


i <- i + 1

further_venues <- GET("https://app.ticketmaster.com/discovery/v2/venues.json?",
                       query = list(apikey = api_key,
                                    countryCode = "DE",
                                    locale = "*",
                                    page = i))
  german_venues <-
    fromJSON(content(german_event_venues, as = "text"))[["_embedded"]][["venues"]]
  full_venue_data[(20 * i - 19):(n), ] <- list.stack(german_venues$Search)

```

**The resulting data frame should look something like this (note that the exact**
**number of search results may have changed since this document has been last**
**modified):**

**glimpse(venue_data)**

## Exercise 5: Visualizing the extracted data

**Below, you can find code that produces a map of Germany. Add points to the **
**map indicating the locations of the event venues across Germany.**

**You will find that some coordinates lie way beyond the German borders and can**
**be assumed to be faulty. Set coordinate values to NA where the value of **
**longitude is outside the range (5.866944, 15.043611) or where the value of**
**latitude is outside the range (47.271679, 55.0846) (these coordinate ranges**
**have been derived from the extreme points of Germany as listed on Wikipedia**
**(see here). For extreme points of other countries, see here).**

```{r map_germany}

ggplot() +
geom_polygon(
aes(x = long, y = lat, group = group), data = map_data("world", region = "Germany"),
fill = "grey90",color = "black") +
theme_void() + coord_quickmap() +
labs(title = "Event locations across Germany", caption = "Source: ticketmaster.com") +
theme(title = element_text(size = 8, face = 'bold'),
plot.caption = element_text(face = "italic"))
```

## Exercise 6: Event locations in other countries

**Repeat exercises 2 to 5 for another European country of your choice. (Hint:**
**Clean code pays off! If you have coded the exercises efficiently, only very **
**few adaptions need to be made.)**

